### 2021-02-24 abstract.tex
Use \acrlong{ml} consistently

This paper describes and evaluates a symbol precedence recommender,
a machine learning system that estimates the best possible precedence
based on observations of prover performance on a set of problems and random precedences.
Using the graph convolutional neural network technology,
the system does not presuppose the problems to be related or share a common signature. 
When coupled with the theorem prover \Vampire{} and evaluated on the \acrshort{tptp} problem library,
the recommender is found to outperform a state-of-the-art heuristic by more than \SI{4}{\percent}
on unseen problems.

>>>>

This paper describes and evaluates a symbol precedence recommender,
a \acrlong{ml} system that estimates the best possible precedence
based on observations of prover performance on a set of problems and random precedences.
Using the graph convolutional neural network technology,
the system does not presuppose the problems to be related or share a common signature. 
When coupled with the theorem prover \Vampire{} and evaluated on the \acrshort{tptp} problem library,
the recommender is found to outperform a state-of-the-art heuristic by more than \SI{4}{\percent}
on unseen problems.

### 2021-02-24 evaluation.tex
Use \acrlong{ml} consistently

\begin{table*}[h]
\caption{
Results of the evaluation of symbol precedence heuristics based on various symbol cost models
on $\ProblemsVal$ ($\card{\ProblemsVal} = 7648$).
Means and standard deviations over 5 runs are reported.
The \gls{gcn} models are trained according to the description in \cref{sec:architecture,sec:training,sec:evaluation}.
The model Simple is the final model from our previous work \cite{DBLP:conf/cade/Bartek020}.
The models that use machine learning for the predicate precedence only
use the \texttt{frequency} heuristic for the function precedence, and vice versa.
The frequency models use the standard \texttt{frequency} heuristic implemented in \Vampire{}.
}
\label{tab:results}
\centering
\begin{tabular}{l|ll|rl}

>>>>

\begin{table*}[h]
\caption{
Results of the evaluation of symbol precedence heuristics based on various symbol cost models
on $\ProblemsVal$ ($\card{\ProblemsVal} = 7648$).
Means and standard deviations over 5 runs are reported.
The \gls{gcn} models are trained according to the description in \cref{sec:architecture,sec:training,sec:evaluation}.
The model Simple is the final model from our previous work \cite{DBLP:conf/cade/Bartek020}.
The models that use \acrlong{ml} for the predicate precedence only
use the \texttt{frequency} heuristic for the function precedence, and vice versa.
The frequency models use the standard \texttt{frequency} heuristic implemented in \Vampire{}.
}
\label{tab:results}
\centering
\begin{tabular}{l|ll|rl}

### 2021-02-24 introduction.tex
Use \acrlong{ml} consistently

In this work, we propose a machine learning system that learns to predict for an ATP
whether one precedence is going to lead to a faster proof search on a given problem than another.
Given a previously unseen problem, it can then be asked to recommend the best possible precedence for an ATP to run with.
Relying only on the logical structure of the problems, % for the learning, 
the system generalizes the knowledge about favorable precedences across problems with different signatures.

>>>>

In this work, we propose a \acrlong{ml} system that learns to predict for an ATP
whether one precedence is going to lead to a faster proof search on a given problem than another.
Given a previously unseen problem, it can then be asked to recommend the best possible precedence for an ATP to run with.
Relying only on the logical structure of the problems, % for the learning, 
the system generalizes the knowledge about favorable precedences across problems with different signatures.

### 2021-02-24 main.tex
Disable the SHRINK mode by default
because we currently fit in 15 pages anyway.
Improve Architecture
Resolve main points by MS. Reference RankNet.
Move training into a dedicated section (out of Architecture).
Use \acrlong{ml} consistently

\newtoggle{SHRINK}
\toggletrue{LONG}
%\togglefalse{SHRINK}

@@

Our previous text \cite{DBLP:conf/cade/Bartek020} marked the initial investigation of applying techniques of \gls{ml}
to generating good symbol precedences.
The neural recommender presented here uses a \gls{gnn} to model symbol costs,
while \cite{DBLP:conf/cade/Bartek020} used a linear combination of symbol features readily available in the \gls{atp} \Vampire{}.
The \gls{gnn}-based approach yields more performant precedences at the cost of longer training and preprocessing time.

@@

\todo[inline]{Related problem: Ranking. See Mohri etc.}

>>>>

\newtoggle{SHRINK}
%\toggletrue{SHRINK}
\togglefalse{SHRINK}

@@

Our previous text \cite{DBLP:conf/cade/Bartek020} marked the initial investigation of applying techniques of \acrlong{ml}
to generating good symbol precedences.
The neural recommender presented here uses a \gls{gnn} to model symbol costs,
while \cite{DBLP:conf/cade/Bartek020} used a linear combination of symbol features readily available in the \gls{atp} \Vampire{}.
The \gls{gnn}-based approach yields more performant precedences at the cost of longer training and preprocessing time.

@@

\todo[inline]{FB: Mention RankNet.}
\todo[inline]{Related problem: Ranking. See Mohri etc.}
